### 2019-06-05 2-Chapters/2-Chapter/chapter2.tex
Waiting for end of simulations

\begin{table}[ht]
    \begin{small}  % WARNING
        \centering
        \begin{tabular}{c|cc|cc}
        \textbf{Algorithms} & $\frac{1}{N} \sum\limits_{j=1}^N [ \sum\limits_{t=1}^{T=100} r^{(j)}_{A(t)}(t) ]$ & $\frac{1}{N} \sum\limits_{j=1}^N [ R^{\cA,(j)}_{T=100} ]$ & $\frac{1}{N} \sum\limits_{j=1}^N [ \sum\limits_{t=1}^{T=10000} r^{(j)}_{A(t)}(t) ]$ & $\frac{1}{N} \sum\limits_{j=1}^N [ R^{\cA,(j)}_{T=10000} ]$ \\
            \hline
            Pure exploration
                & $51$ & $19$
                & $XXX$ & $XXX$ \\
            Pure exploitation
                & $62$ & $8.3$
                & $XXX$ & $XXX$ \\
            \hline
            $\varepsilon$-greedy
                & $51$ & $18.7$
                & $XXX$ & $XXX$ \\
            Explore-then-Commit
                & $57$ & $12.9$
                & $XXX$ & $XXX$ \\
            \hline
            $\UCB_1$
                & $\mathbf{60}$ & $\mathbf{9.8}$
                & $XXX$ & $XXX$ \\
            \klUCB{}
                & $61$ & $9.3$
                & $XXX$ & $XXX$ \\
            \hline
            Thompson sampling
                & $\mathbf{60}$ & $\mathbf{9.6}$
                & $XXX$ & $XXX$ \\
            \hline
        \end{tabular}
        \caption{Cumulated rewards and regret, for horizons $T=100$ and $T=10000$, \emph{averaged over $N=1000$ independent simulations}, for different algorithms.}
        \label{table:2:meanResults}
    \end{small}  % WARNING
\end{table}

% FIXME generate at the end of the simulation
\begin{figure}[h!]  % [htbp]
	% \centering
	\includegraphics[width=1.00\linewidth]{meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT100N1000.pdf}
	\caption{Mean cumulated rewards as function of the current time step $t$ for horizon $T=100$ and $N=1000$ independent runs, for different algorithms }
	\label{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT100N1000}
\end{figure}

% FIXME generate at the end of the simulation
\begin{figure}[h!]  % [htbp]
	% \centering
	\includegraphics[width=1.00\linewidth]{meanRegretAsFunctionOfTimeForDifferentAlgorithmsT100N1000.pdf}
	\caption{Mean regret $R_t$ as function of $t$ for $T=100$ and $N=1000$.}
	\label{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT100N1000}
\end{figure}

@@

We also include in Figures~\ref{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT100N1000}, \ref{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT100N1000}, \ref{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT10000N1000}, \ref{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT10000N1000} below the mean cumulated rewards and mean regret as functions of the current time step $t$, for $T=100$ then $T=10000$ for $N=1000$ independent runs.

>>>>

% Final ranking for this environment #0 : (using more accurate estimate of the regret)
% - Policy 'Pure exploration'     was ranked      7 / 7 for this simulation
%         (last regret = 1891.1,  total regret = 1900.5,  total reward = 5099,    total weighted selection = 5099.5).
% - Policy 'Pure exploitation'    was ranked      5 / 7 for this simulation
%         (last regret = 649.98,  total regret = 653.2,   total reward = 6348.6,  total weighted selection = 6346.8).
% - Policy '$\varepsilon$-greedy' was ranked      4 / 7 for this simulation
%         (last regret = 540.54,  total regret = 541.9,   total reward = 6460.7,  total weighted selection = 6458.1).
% - Policy 'Explore-then-Exploit' was ranked      6 / 7 for this simulation
%         (last regret = 1207.1,  total regret = 1207.1,  total reward = 5794.9,  total weighted selection = 5792.9).
% - Policy 'UCB($\alpha=1$)'      was ranked      3 / 7 for this simulation
%         (last regret = 79.435,  total regret = 79.513,  total reward = 6920.9,  total weighted selection = 6920.5).
% - Policy 'Bernoulli kl-UCB'     was ranked      2 / 7 for this simulation
%         (last regret = 72.274,  total regret = 72.368,  total reward = 6927.5,  total weighted selection = 6927.6).
% - Policy 'Thompson sampling'    was ranked      1 / 7 for this simulation
%         (last regret = 49.366,  total regret = 49.402,  total reward = 6951.4,  total weighted selection = 6950.6).

\begin{table}[ht]
    \begin{small}  % WARNING
        \centering
        \begin{tabular}{c|cc|cc}
        \textbf{Algorithms} & $\frac{1}{N} \sum\limits_{j=1}^N \sum\limits_{t=1}^{T=100} r^{(j)}_{A(t)}(t)$ & $\frac{1}{N} \sum\limits_{j=1}^N R^{\cA,(j)}_{T=100}$ & $\frac{1}{N} \sum\limits_{j=1}^N \sum\limits_{t=1}^{T=10000} r^{(j)}_{A(t)}(t)$ & $\frac{1}{N} \sum\limits_{j=1}^N R^{\cA,(j)}_{T=10000}$ \\
            \hline
            Pure exploration
                & $51$ & $19$
                & $5099$ & $1900$ \\
            Pure exploitation
                & $62$ & $8.3$
                & $6349$ & $653$ \\
            \hline
            $\varepsilon$-greedy
                & $51$ & $18.7$
                & $6460$ & $542$ \\
            Explore-then-Commit
                & $57$ & $12.9$
                & $5795$ & $1207$ \\
            \hline
            $\UCB_1$
                & $\mathbf{60}$ & $\mathbf{9.8}$
                & $6921$ & $79$ \\
            \klUCB{}
                & $61$ & $9.3$
                & $6927$ & $72$ \\
            \hline
            Thompson sampling
                & $\mathbf{60}$ & $\mathbf{9.6}$
                & $\mathbf{6951}$ & $\mathbf{49}$ \\
            \hline
        \end{tabular}
        \caption{Cumulated rewards and regret, for horizons $T=100$ and $T=10000$, \emph{averaged over $N=1000$ independent simulations} ($j=1,\dots,N$), for different algorithms.}
        \label{table:2:meanResults}
    \end{small}  % WARNING
\end{table}

% % FIXME generate at the end of the simulation
% \begin{figure}[h!]  % [htbp]
% 	% \centering
% 	\includegraphics[width=1.00\linewidth]{meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT100N1000.pdf}
% 	\caption{Mean cumulated rewards as function of the current time step $t$ for horizon $T=100$ and $N=1000$ independent runs, for different algorithms }
% 	\label{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT100N1000}
% \end{figure}

% % FIXME generate at the end of the simulation
% \begin{figure}[h!]  % [htbp]
% 	% \centering
% 	\includegraphics[width=1.00\linewidth]{meanRegretAsFunctionOfTimeForDifferentAlgorithmsT100N1000.pdf}
% 	\caption{Mean regret $R_t$ as function of $t$ for $T=100$ and $N=1000$.}
% 	\label{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT100N1000}
% \end{figure}

@@

We also include in Figures
% \ref{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT100N1000}, \ref{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT100N1000},
\ref{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT10000N1000}, \ref{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT10000N1000} below the mean cumulated rewards and mean regret as functions of the current time step $t$, for $T=10000$ for $N=1000$ independent runs.
The reward of the best arm is also plotted in Figure~\ref{fig:2:meanRewardsAsFunctionOfTimeForDifferentAlgorithmsT10000N1000}, to illustrate convergence of the average reward $\frac{1}{t} \sum\limits_{s=1}^t r_{A(s)}(s)$, which should converge to $\mu^*$ when $t\to\infty$ (or $t\toT$) for efficient algorithms.
Conversely, we also add the Lai \& Robbins' logarithmic lower-bound on regret ($C_I \log(t)$ from case 2 of Theorem~\ref{thm:2:forSecondLogTLowerBound}) on the regret plot in Figure~\ref{fig:2:meanRegretAsFunctionOfTimeForDifferentAlgorithmsT10000N1000}.
%
We can clearly identify the behavior of the different strategies:
the three efficient strategies indeed achieve a sub-linear regret, that looks logarithmic as supported by the theory,
while the naive strategies achieve linear regret.
The two simple strategies also achieve sub-linear regret but are less efficient:
both $\varepsilon$-greedy and Explore-then-Commit starts as pure exploration, respectively until $\varepsilon_0/t$ becomes smaller than $1$ and until $t > T_0$, then they almost always correctly identify the best arm and start to catch up with the best policies.
